Online Verification of Commutativity

### 2020-06-07 acmPaper/paper.tex
Capitalize titles
A bit about currency graph

\documentclass[sigconf,authordraft]{acmart}
%
\usepackage{tikz}
\usepackage{amssymb}
\usepackage{algorithm}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\begin{document}
\settopmatter{printacmref=false}
\title{Online verification of Commutativity}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author}
\email{email}
\author{Second Author}
\authornotemark[1]
\email{email 2}
\affiliation{%
  \institution{Cornell University}
  \streetaddress{address}
  \city{Ithaca}
  \state{New York}
  \postcode{14850}
}

@@

>>>>

\documentclass[sigplan,review,anonymous]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usepackage{amssymb}
\usepackage{algorithm}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\begin{document}
\settopmatter{printacmref=false}
\title{Online Verification of Commutativity}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author}
\email{email}
\author{Second Author}
\authornotemark[1]
\email{email 2}
\affiliation{%
  \institution{Cornell University}
  \streetaddress{address}
  \city{Ithaca}
  \state{New York}
  \postcode{14850}
}

@@

To demonstrate our algorithm applied to a real world situation, 
we found inconsistencies in a diagram of the exchange rate between currencies.
Consider a diagram with nodes as currencies and a directed edge being the
conversion rate from its source node's currency to its sink node's currency.
Since the transformation exchange rate of money from any given base currency to a target currency
can be expected to be the same regardless of which intermediate currency transformations
are used, this diagram should commute.

Using an api, https://exchangeratesapi.io, we built a fully connected diagram for 32 currencies.
To ensure that it indeed commuted, before the addition of each edge, we used the algorithms presented
to ensure the addition of a new edge did not introduce inconsistencies in the existing diagram.
If a new edge was, in fact, problematic, the algorithm returned an example inconsistent
pair that would arise from the addition of the edge.
The pair would consist of two currency transformation sequences with the 
same source currency and ultimate destination currency, but with different effective 
exchange rates values, as computed by taking the product of all the exchange rates
encountered through the chain.

We allowed an "error tolerance" for floating point error.
Graphs were generally consistent up to an error tolerance to the order of magnitude $10^{-6}$.
However, below this threshold we found inconsistencies.
For both algorithms, computation completed in minutes.
